Flexibility of interactions depends on habitat suitability

### 2019-07-28 paper/manuscript.Rmd
Some more notes and ideas

@@

Conclusion: Biotic inetractions are def important at determining abundace. They observed positive effects of biotic interactions at colder climates (low suitability for plants) -- suggest facilitation. and negative effects of interactions at warmer climates (high suitability) suggesting competition. *Should I calculate the suitability of other species?*

@@

Most BI-SDMs assume that biotic interactions are constant in space and time. It is more likely, however, that interaction strengths are modulated by the biotic and abiotic environment. Experimental studies showed that rates of biological interactions depend on environmental conditions: rates of herbivory are temperature dependent (Burnside, Erhardt, Hammond, & Brown, 2014); mycorrhizal symbioses change with resource availability (Cox, Barsoum, Lilleskov, & Bidartondo, 2010; Johnson, Wilson, Bowker, Wilson, & Miller, 2010); and plant–plant interactions can shift from competitive to facilitative along a stress gra- dient (Bertness & Callaway, 1994). Additionally, environmental change can modulate biotic interactions via phenological mismatches, such as for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007). In these conditions, the model must also allow for the interplay of envi- ronmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).

>>>>

**Is my central topic turnover of interactions**?

**Continuation: compare the suitability of the species that species do not interact with vs those that interact (when a possible interaction occurs but is not realised)?**

**Continuation: average suitability of all species. If avg. competitors suitability is low, species, facilitation more common and resource sharing should increase. If avg. suitability is high, the opposite should happen?**

**SHould I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**

@@

Conclusion: Biotic inetractions are def important at determining abundace. They observed positive effects of biotic interactions at colder climates (low suitability for plants) -- suggest facilitation. and negative effects of interactions at warmer climates (high suitability) suggesting competition. *Should I calculate the suitability of other species and test this?*

@@

Most BI-SDMs assume that biotic interactions are constant in space and time. It is more likely, however, that interaction strengths are modulated by the biotic and abiotic environment. Experimental studies showed that rates of biological interactions depend on environmental conditions: rates of herbivory are temperature dependent (Burnside, Erhardt, Hammond, & Brown, 2014); mycorrhizal symbioses change with resource availability (Cox, Barsoum, Lilleskov, & Bidartondo, 2010; Johnson, Wilson, Bowker, Wilson, & Miller, 2010); and plant–plant interactions can shift from competitive to facilitative along a stress gra- dient (Bertness & Callaway, 1994). Additionally, environmental change can modulate biotic interactions via phenological mismatches, such as for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007). In these conditions, the model must also allow for the interplay of environmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).

**From Gravel et al. 2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions. Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure. *Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe*

There is, however, ample evidence that interaction networks vary in space and time (Laliberté and Tylianakis 2010, Poisot et al. 2012, 2016c, Schleuning et al. 2012, Albouy et al. 2014, Trøjelsgaard et al. 2015), even though there is no common framework with which to generalize these results.

he occurrence and intensity of interactions could vary because of the environment, species abundance, and higher- order ecological interactions (Poisot et al. 2015). *Well do I show that could vary because of more stuff?*

Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- action distribution may well respond to diferent drivers (Poisot et al. 2012).
